The LBRY Trending Algorithm

### 2021-11-17 tex/ms.tex
Define squashed plus

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[left=1.5cm, right=1.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{natbib}
\newcommand{\logsumexp}{\textnormal{logsumexp}}
\newcommand{\logdiffexp}{\textnormal{logdiffexp}}

@@

To compute updated trending scores, we need to add values, but on the
squashed grade. In other words, if we have squashed values $S(x)$ and
$S(y)$, we will need the squashed sum
\begin{align}
S(U(x) + U(y)).
\end{align}
These can be worked out in terms of logsumexp and logdiffexp.

@@

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[left=1.5cm, right=1.5cm, bottom=2cm, top=2cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{natbib}
\newcommand{\logsumexp}{\textnormal{logsumexp}}
\newcommand{\logdiffexp}{\textnormal{logdiffexp}}
\newcommand{\sign}{\textnormal{sign}}

@@

To compute updated trending scores, we need to add and multiply
values, but on the
squashed grade. In other words, if we have squashed values $x$ and
$y$, we will need the squashed sum
\begin{align}
x \oplus y &= S(U(x) + U(y))
\end{align}
and the squashed product
\begin{align}
x \otimes y &= S(U(x)U(y)).
\end{align}
These can be worked out in terms of logsumexp and logdiffexp.
The results are fairly complicated and are given in the Appendix.

@@

\appendix
\section{Squashed Arithmetic}
The squashed addition operator is broken down into four cases, depending
on the sign of the arguments:
\begin{align}
x \oplus y &= \left\{
    \begin{array}{lr}
   -\logsumexp(-x, \logdiffexp(-y, 0)),& x < 0~\textnormal{and}~y < 0, \\
    \logsumexp(x, \logdiffexp(y, 0)),& x \geq 0~\textnormal{and}~y \geq 0 \\
    \logsumexp(0, \logdiffexp(x, -y)), & \sign(x) \neq \sign(y)~\textnormal{and}~|x| \geq |y|\\
    -\logsumexp(0, \logdiffexp(-y, x)), & \sign(x) \neq \sign(y)~\textnormal{and}~|x| < |y|
    \end{array}
\right. .
\end{align}
